% CREATED BY DAVID FRISK, 2015
\section*{Appendix: Interview and evaluation questions}

\subsection*{Semi-structured interview questions} 

 \begin{enumerate}
  \item What is the translation process of the SSIM to semantics that your company understands?
  \item In your experience, can you give us examples where a field inside the SSIM was used in a different way from customer to customer? That is, customers had their own interpretation of that field? And why does this happen?
  
  
  
  
  \item What about with misinterpretations of the semantics, what could go wrong? And how often can it occur?
  \item What would you ask your customers to elicit their use cases?
  \item Tell us, according to your experiences, about parts of the IATA that could be misinterpreted, that could maybe be handled differently from different customers?
  
  \item How did you manage these issues in the past? 
  \item How are you handling things right now? Do you think there are issues with the current approach?

   
 \end{enumerate}



\subsection*{Group interview questions} 

For each of the following variation points we found during our analysis phase: \\

\begin{enumerate}
  \item  Do you agree that they are indeed a variation point?
  \item  Is there something else that we might have missed?
  \item What do you think is the most urgent to deal with? 
  
  
  \end{enumerate}

\subsection*{Code analysis questions} 

\begin{enumerate}
\item Can you guide us through the SSIM integrator's code of the old system?
\item Can you talk a little about the special cases the integrator is handling?
\item Can you elaborate more about special cases of your customers?
\item Do you have other issues with the interpretations of the semantics?
\item How do you detect these misinterpretations? and how do you handle them?

  \end{enumerate}

\subsection*{First evaluation questions}



\begin{enumerate}
\item The functions that you wrote for your current customer in the new system, do you think they can be reused by some other airline?

\item Do you think, in general, that certain use cases might appear to other customers?

\item (after presenting our suggested method) Do you think this approach is good or bad? Why? 

\item Are there some other ways that you could suggest for handling customer specific use cases?

\item Do you think this method could be replicated to other contexts as well?

\item Would you consider integrate this?

  \end{enumerate}

\subsection*{Final evaluation questions} 
\begin{enumerate}
\item What do you think of this approach? And Why? Do you agree with the preliminary feedback? 

\item Do you think use recurring customer specific use cases could emerge for the SSIM interface? What about other interfaces? 

\item What guarantee you have that your customers will write quality code and that their systems will be compatible with yours? 

\item How do your customers understand the system's core and how do they test it?

\item Do you agree with these guidelines? And Why? Is there something missing? 

\item (after discussing variability management for the Operational Messages interface) Do you agree with this approach? And Why? 

\item What do you think about possible future work? What other ways could support the understanding and effective management of variability? 


  \end{enumerate}


